---
title: "Consulting Project"
author: "Jong Hyun Choi"
date: "10/17/2021"
output: html_document
---

```{r}
data4 = read_xlsx("C:\\Users\\SAMSUNG\\OneDrive\\STAT4983W\\ConsultingProjectData_v3.xlsx", sheet = "All_data_Categories")
data2 = read_xlsx("C:\\Users\\SAMSUNG\\OneDrive\\STAT4983W\\ConsultingProjectData_v3.xlsx", sheet = "Plots_data")
data3 = read_xlsx("C:\\Users\\SAMSUNG\\OneDrive\\STAT4983W\\ConsultingProjectData_v3.xlsx", sheet = "Seedlings_cut_sprouting_togethe")
```


```{r}
yesharvest  = subset(data1, Harvested %in% 1)
yesharvest = yesharvest$Harvested
```

```{r}
par(mfrow=c(2,3))
boxplot(data4$`BasalArea of plot m2 ha-1` ~ data4$VegetationType)
boxplot(data4$`BasalArea of plot m2 ha-1` ~ data4$Harvested)
boxplot(data4$`BasalArea of plot m2 ha-1` ~ data4$`Milpa(has it been milpa)`)
boxplot(data4$`BasalArea of plot m2 ha-1` ~ data4$`Forest'sAge (years)`)
boxplot(data4$`BasalArea of plot m2 ha-1` ~ data4$SoilType)
```


ggplot(data2, aes(x=`Basal Area (m2/ha-1)`, y=Harvested)) +  geom_boxplot(fill='blue')
ggplot(data2, aes(x=`Basal Area (m2/ha-1)`, y=VegetationType)) +  geom_boxplot(fill='green')
ggplot(data2, aes(x=`Basal Area (m2/ha-1)`, y=SoilType)) +  geom_boxplot(fill='red')
ggplot(data2, aes(x=`Basal Area (m2/ha-1)`, y=`Milpa(has it been milpa)`)) + geom_boxplot(fill='yellow')
ggplot(data2, aes(x=`Basal Area (m2/ha-1)`, y=`Forest'sAge (years)`)) +  geom_boxplot(fill='black')


### interation???
```{r}
## We want to see if there is significant difference between the Basal Area of plot m^2 ha^-1 and whether it's been milpa or not. 
# Significance level less than 0.05 
summary(aov(data4$`BasalArea of plot m2 ha-1` ~ milpa, data = data4))
```

```{r}
summary(aov(data4$`BasalArea of plot m2 ha-1` ~ data4$VegetationType))
summary(aov(data4$`BasalArea of plot m2 ha-1` ~ data4$Harvested))
summary(aov(data4$`BasalArea of plot m2 ha-1` ~ data4$SoilType))
summary(aov(data4$`BasalArea of plot m2 ha-1` ~ data4$`Forest'sAge (years)`))
summary(aov(data4$`BasalArea of plot m2 ha-1` ~ data4$`Milpa(has it been milpa)`))

```



## 2
```{r}
par(mfrow=c(2,3))
boxplot(data2$`Stem density (#/ha)` ~ data2$Harvested)
boxplot(data2$`Stem density (#/ha)` ~ data2$VegetationType)
boxplot(data2$`Stem density (#/ha)` ~ data2$`Milpa(has it been milpa)`)
boxplot(data2$`Stem density (#/ha)` ~ data2$`Forest'sAge (years)`)
boxplot(data2$`Stem density (#/ha)` ~ data2$SoilType)
```

##statistically different? 
## what does the pvalue mean? 


```{r}
summary(aov(data2$`Stem density (#/ha)` ~ data2$Harvested))
summary(aov(data2$`Stem density (#/ha)` ~ data2$`Milpa(has it been milpa)`))
summary(aov(data2$`Stem density (#/ha)` ~ data2$VegetationType))
summary(aov(data2$`Stem density (#/ha)` ~ data2$SoilType))
summary(aov(data2$`Stem density (#/ha)` ~ data2$`Forest'sAge (years)`))
```

```{r}
TukeyHSD(aov(data2$`Stem density (#/ha)` ~ data2$VegetationType))


```


```{r}
## number of stems in each size class 
seedling = filter(data1, `DBH (cm)` < 0.5) 
seedlingcount = length(seedling$`DBH (cm)`)

sapling = filter(data1, `DBH (cm)` >= 0.5 & `DBH (cm)` < 5)
saplingcount = length(sapling$`DBH (cm)`)

tree = filter(data1, `DBH (cm)` > 4)
treecount = length(tree$`DBH (cm)`)
```



```{r}
data4 %>% filter(Type %in% c("Sapling", "Tree")) %>%  
ggplot(aes(x = Harvested, y = `DBH (cm)`, group = Type, color = Type)) + geom_boxplot()


data4 %>% filter(Type %in% c("Sapling", "Tree (11~15)", "Tree (16~20)", "Tree (21~25)", "Tree (26~30)", "Tree (5~10)")) %>%  
ggplot(aes(x = Harvested, y = `Stem #`, group = Type, color = Type)) + geom_boxplot()
```







4.	Are these population size structures (stem densities per size class) statistically different between harvested and unharvested plots? Are there other variables influencing this difference? 

```{r}
summary(aov(lm(data2$`Saplings (#/ha)` ~ data2$Harvested * data2$SoilType)))

summary(aov(data2$`Saplings (#/ha)` ~ data2$Harvested * data2$VegetationType))

summary(aov(data2$`Saplings (#/ha)` ~ data2$Harvested *data2$`Milpa(has it been milpa)` ))

summary(aov(data2$`Saplings (#/ha)` ~ data2$Harvested *data2$`Forest'sAge (years)` ))



summary(aov(data2$`Saplings (#/ha)` ~ data2$Harvested))
summary(aov(data2$`Saplings (#/ha)` ~ data2$SoilType))
summary(aov(data2$`Saplings (#/ha)` ~ data2$VegetationType))
summary(aov(data2$`Saplings (#/ha)` ~ data2$`Milpa(has it been milpa)`))
summary(aov(data2$`Saplings (#/ha)` ~ data2$`Forest'sAge (years)`))






summary(aov(data2$`Tree (#/ha)` ~ data2$SoilType))
summary(aov(data2$`Tree (#/ha)` ~ data2$VegetationType))
summary(aov(data2$`Tree (#/ha)` ~ data2$`Milpa(has it been milpa)`))
summary(aov(data2$`Tree (#/ha)` ~ data2$`Forest'sAge (years)`))
summary(aov(data2$`Tree (#/ha)` ~ data2$Harvested))






summary(aov(data2$`Sapling Basal Area (m2/ha-1)` ~ data2$Harvested))

summary(aov(data2$`Sapling Basal Area (m2/ha-1)` ~ data2$VegetationType))




summary(aov(data2$`Sapling Basal Area (m2/ha-1)` ~ data2$`Milpa(has it been milpa)`))




summary(aov(data2$`Sapling Basal Area (m2/ha-1)` ~ data2$`Forest'sAge (years)`))



summary(aov(data2$`Sapling Basal Area (m2/ha-1)` ~ data2$SoilType))



summary(aov(data2$`Tree Basal Area` ~ data2$Harvested))
summary(aov(data2$`Tree Basal Area` ~ data2$VegetationType))
summary(aov(data2$`Tree Basal Area` ~ data2$`Milpa(has it been milpa)`))
summary(aov(data2$`Tree Basal Area` ~ data2$`Forest'sAge (years)`))
summary(aov(data2$`Tree Basal Area` ~ data2$SoilType))


```

> col2=ifelse(df1$col=="true",1,0)

plot(partyHr ~ drinks, data=survey, col=as.integer(gender), xlab="Drinks/week", 
     ylab="Party hours/week", pch=19, las=1)
abline(fit_male$coefficients, col=1, lwd=2)
abline(fit_female$coefficients, col=2, lwd=2)





as.numeric(as.factor(weather4$RainTomorrow))


require(dplyr)
weather4 <- weather4 %>%
      mutate(RainToday = ifelse(RainToday == "No",0,1))
      
      
```{r}
data5 = data2 %>% mutate(Harvested = ifelse(Harvested == "Yes", 1, 0))
boxplot(data5$`Saplings (#/ha)` ~ data5$Harvested)



boxplot(data4$`BasalArea per tree m2 ha-1` ~ data4$Type)

```



```{r}
par(mfrow=c(2,3))

g = ggplot(data4, aes(x = Type, y = `Stem #`))
g + geom_bar(aes(fill = Harvested), stat = 'identity') 

j = ggplot(data4, aes(x = Type, y = `Stem #`))
j + geom_bar(aes(fill = SoilType), stat = 'identity')

z = ggplot(data4, aes(Type, y = `Stem #`))
z + geom_bar(aes(fill = VegetationType), stat = 'identity')

x = ggplot(data4, aes(Type, y = `Stem #`))
x + geom_bar(aes(fill = `Milpa(has it been milpa)`), stat = 'identity')

t = ggplot(data4, aes(Type, y= `Stem #`))
t + geom_bar(aes(fill = `Forest'sAge (years)`), stat = 'identity')

```


```{r}
par = 
h = ggplot(data4, aes(x = Type, y = `BasalArea per tree m2 ha-1`))
h + geom_bar(aes(fill = Harvested), stat = 'identity') 

l = ggplot(data4, aes(x = Type, y = `BasalArea per tree m2 ha-1`))
l + geom_bar(aes(fill = SoilType), stat = 'identity')

c = ggplot(data4, aes(Type, y = `BasalArea per tree m2 ha-1`))
c + geom_bar(aes(fill = VegetationType), stat = 'identity')

d = ggplot(data4, aes(Type, y = `BasalArea per tree m2 ha-1`))
d + geom_bar(aes(fill = `Milpa(has it been milpa)`), stat = 'identity')

s = ggplot(data4, aes(Type, y= `BasalArea per tree m2 ha-1`))
s + geom_bar(aes(fill = `Forest'sAge (years)`), stat = 'identity')
```


library(ggplot2)
data(Marriage, package = "mosaicData")

# plot the distribution of race
ggplot(Marriage, aes(x = race)) + 
  geom_bar()
  
  
  
  
  data(Salaries, package="carData")

# calculate mean salary for each rank
library(dplyr)
plotdata <- Salaries %>%
  group_by(rank) %>%
  summarize(mean_salary = mean(salary))

# plot mean salaries
ggplot(plotdata, 
       aes(x = rank, 
           y = mean_salary)) +
  geom_bar(stat = "identity")



```{r}
plotdat = data4 %>% group_by(Type, SoilType) %>% summarize(Stem_density = `Stem #`) 
ggplot(plotdat, aes(x = Type, y = Stem_density, group = SoilType)) + geom_bar(stat = "identity")

plotdat2 = data4 %>% group_by(Type) %>% summarize(DBH = `DBH (cm)`)
ggplot(plotdat2, aes(x = Type, y = DBH)) + geom_bar(stat = 'identity')
```








